---
title: "R Notebook"
output: html_notebook
---

This chunk loads all data and sets up the data frames
```{r}
library(jsonlite)
library(binr)
library(caret)
library(matlib)

library(ggplot2)
library(tidyr)
library(ggthemes)

library(doMC)
registerDoMC(cores = 12)

read_all_json_files <- function(base_path) {
  meta_files = list.files(path=base_path, pattern = "*.json", recursive = TRUE)

  meta_data <- list()
  for (i in seq_along(meta_files)) {
    meta_data[[i]] <- fromJSON(paste(base_path,meta_files[i], sep=""))
    meta_data[[i]] <- c(meta_data[[i]], meta_path=dirname(meta_files[i]))
    # meta_data[[i]] <- rbind(meta_data[[i]], c(meta_files[i]))
  }
  
  return(meta_data)
}


base_path <- '~/dev/owlspringembedder/results/'

meta_frames <- read_all_json_files(base_path)

Iteration <- c()
Elapsed <- c()
TimeAttractiveForces <- c()
TimeRepulsive <- c()
TimeDisperse <- c()
TimeBuild <- c()
TimeTraverse <- c()
Mode <- c()
Scene <- c()

for(frame in meta_frames) {
  Iteration <- c(Iteration, frame$Iteration[[2]])
  Elapsed <- c(Elapsed, frame$Elapsed[[2]])
  TimeAttractiveForces = c(TimeAttractiveForces, frame$TimeAttractiveForces[[2]])
  TimeRepulsive = c(TimeRepulsive, as.numeric(frame$TimeRepulsiveForce[[2]]))
  TimeDisperse = c(TimeDisperse, frame$TimeDisperse[[2]])
  TimeBuild = c(TimeBuild, frame$TimeBuild[[2]])
  TimeTraverse = c(TimeTraverse, frame$TimeTraverse[[2]])
  
  Mode = c(Mode, rep(frame$mode, times=length(frame$TimeTraverse[[2]])))
  
  Scene = c(Scene, rep(frame$scene, times=length(frame$TimeTraverse[[2]])))
}

#Create new data frame
dfA <- data.frame(Iteration, Elapsed, TimeAttractiveForces, TimeDisperse, TimeRepulsive, Mode, Scene)

#Compute mean to inspect data
mean(dfA[dfA$Mode=="lbvh",]$Elapsed)


####### Table with means


Elapsed <- c()
TimeBuild <- c()
TimeTraverse <- c()
Mode <- c()
Scene <- c()
NumNodes <- c()

for(frame in meta_frames) {
  Elapsed <- c(Elapsed, mean(frame$Elapsed[[2]]))
  TimeBuild = c(TimeBuild, mean(frame$TimeBuild[[2]]))
  TimeTraverse = c(TimeTraverse, mean(frame$TimeTraverse[[2]]))
  Mode = c(Mode, frame$mode)
  #NumNodes <- c(NumNodes, frame$NumNodes[[2]][[1]])
  Scene = c(Scene, frame$scene)
}

#Create new data frame
dfMeans <- data.frame(Elapsed, TimeBuild, TimeTraverse, Mode, Scene)

###########

Time <- c()
Type <- c()
Mode <- c()
Scene <- c()

for(frame in meta_frames) {
  Time = c(Time, frame$TimeAttractiveForces[[2]])
  lAttr = length(frame$TimeAttractiveForces[[2]])
  Type = c(Type, rep("Attractive",lAttr))
  
  Time = c(Time, frame$TimeDisperse[[2]])
  lDisp = length(frame$TimeDisperse[[2]])
  Type = c(Type, rep("Disperse",lDisp))
  
  Time = c(Time, as.numeric(frame$TimeRepulsiveForce[[2]]))
  lRep = length(frame$TimeRepulsiveForce[[2]])
  Type = c(Type, rep("Repulsive",lRep))
  
  lTotal <- lAttr + lDisp + lRep
  
  Mode = c(Mode, rep(frame$mode, times=lTotal))
  Scene = c(Scene, rep(frame$scene, times=lTotal))
}

#Create new data frame
dfTimeStage <- data.frame(Time, Type, Mode, Scene)


Time <- c()
Type <- c()
Scene <- c()
Mode <- c()
NumNodes <- c()

for(frame in meta_frames) {
TimeBuild = c(TimeBuild, frame$TimeBuild[[2]])
TimeTraverse = c(TimeTraverse, frame$TimeTraverse[[2]])

  Time = c(Time, frame$TimeBuild[[2]])
  lBuild = length(frame$TimeBuild[[2]])
  Type = c(Type, rep("Build",lBuild))
  
  Time = c(Time, frame$TimeTraverse[[2]])
  lTrav = length(frame$TimeTraverse[[2]])
  Type = c(Type, rep("Traverse",lTrav))
  
  NumNodes = c(NumNodes, frame$NumNodes[[2]])
  
  lTotal <- lBuild + lTrav
    
  Mode = c(Mode, rep(frame$mode, times=lTotal))
  Scene = c(Scene, rep(frame$scene, times=lTotal))
}


dfTimeBuildTraverse <- data.frame(Time, Type, Mode, Scene, NumNodes)
```

Box plot total run times 
```{r}
library(binr)
library(caret)
library(plyr)

addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

t <-  theme(axis.text.x=element_text(size=22,face="bold"),
        axis.text.y=element_text(size=22,face="bold"),
        axis.title=element_text(size=26,face="bold"),
        legend.title = element_text(size=22,face="bold"),
        legend.text=element_text(size=20,face="bold"),
        strip.text.x = element_text(size = 22,face="bold"),
        plot.title = element_text(size=24,face="bold")
        )  

boxplot_elapsed <- function(dfAScene) {
  
    p <- ggplot(data=dfScene, aes(x=dfScene$Mode, y=dfScene$Elapsed)) + 
          geom_boxplot(width=0.9
                       , outlier.shape = NA
                       ) +
          stat_boxplot(geom ='errorbar', width = 0.6) +
          labs(x="Mode", y="Time(ms)")  + 
          ggtitle("") +
     #   stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="darkred", fill="red") +
    #    stat_summary(fun.y=mean, colour="darkred", size=10, geom="text", show_guide = FALSE,  vjust=-1.0, aes( label=round(..y.., digits=5))) +
      stat_boxplot(geom ='errorbar', width = 0.6) +
     t +
      theme(legend.position = "none")
    
    
  ggstat.data <- ggplot_build(p)$data
  ggwhisk1 <- ggstat.data[[1]]$ymax
  
  meanV.naive = round(mean(dfScene[dfScene$Mode=="Naive",]$Elapsed), digits=5)
  meanV.lbvh = round(mean(dfScene[dfScene$Mode=="LBVH",]$Elapsed), digits=5)
  meanV.rtx = round(mean(dfScene[dfScene$Mode=="RTX\n(Ours)",]$Elapsed), digits=5)
  
  meanV <- c(meanV.naive, meanV.lbvh, meanV.rtx)
  
  modeLevels <- levels(dfScene$Mode)  
  dfWhisker <- data.frame(mean = meanV, whisk = ggwhisk1, levels = modeLevels)
  
  q1 = bquote(bar("t")~"="~.(round(dfWhisker$mean[[1]], digits=3)))
  q2 = bquote(bar("t")~"="~.(round(dfWhisker$mean[[2]], digits=3)))
  q3 = bquote(bar("t")~"="~.(round(dfWhisker$mean[[3]], digits=3)))
  
  p <- p +
    stat_summary(fun.y=mean, geom="point", shape=20, size=10, color="darkred", fill="red") +
    geom_text(data = dfWhisker, size = 10, aes(x = levels, y = whisk, 
     # label = sprintf("%s%f", "expression(paste(\"Oh how I wish \", underline(underlining))),",dfWhisker$mean), colour="red",vjust = -.5), parse=TRUE)
      label = c(q1,q2,q3), colour="darkred",vjust = -.5), parse=TRUE)
   
  return(p)
}

#dfScene = dfA[dfA$Scene=="gephi-100k",]
scenes <- c("gephi-100k", "k-5-10-connected", "k-5-10-unconnected", "tree16")

dfARen <- dfA

#Convert to miliseconds
dfARen$Elapsed = dfARen$Elapsed * 1000  

#Sort factor levels in plot
dfARen$Mode <- factor(dfARen$Mode, levels = c('naive','lbvh','rtx'),ordered = TRUE)

#Rename factor levels

dfARen$Mode <- revalue(dfARen$Mode, c("naive"="Naive", "lbvh"="LBVH", "rtx" = "RTX\n(Ours)"))

###gephi-100k
sceneName <- scenes[1]
dfScene = dfARen[dfARen$Scene==sceneName,]
  
p <- boxplot_elapsed(dfScene)
p <- p + coord_cartesian(ylim = c(0, 65.00))
    
print(p)
ggsave(paste(sceneName, ".pdf", sep=""), p)
  
  
###k-5-10-connected

sceneName <- scenes[2]
dfScene = dfARen[dfARen$Scene==sceneName,]
  
p <- boxplot_elapsed(dfScene)
p <- p + coord_cartesian(ylim = c(0, 24.0))
    
print(p)
ggsave(paste(sceneName, ".pdf", sep=""), p)

 
###k-5-10-unconnected

sceneName <- scenes[3]
dfScene = dfARen[dfARen$Scene==sceneName,]
  
p <- boxplot_elapsed(dfScene)
p <- p + coord_cartesian(ylim = c(0, 900.0))
    
print(p)
ggsave(paste(sceneName, ".pdf", sep=""), p)


###tree16
sceneName <- scenes[4]
dfScene = dfARen[dfARen$Scene==sceneName,]

p <- boxplot_elapsed(dfScene)
p <- p + coord_cartesian(ylim = c(0, 240.0))
  
print(p)
ggsave(paste(sceneName, ".pdf", sep=""), p)


```



Box plot runtime steps of all scenes
```{r}
library(binr)
library(caret)

stages <- c("Attractive","Disperse", "Repulsive")

scene_labeller <- function(variable,value){
  return(stages[value])
}

ggplot(data=dfTimeStage, aes(x=dfTimeStage$Mode, y=dfTimeStage$Time, fill=dfTimeStage$Mode))  + 
  geom_boxplot(width=0.9) +facet_grid(. ~ Type, labeller = scene_labeller) +
  theme(panel.spacing = unit(0.15, "lines")) +
     guides(fill=FALSE)+
    labs(x="Implementation", y="Time(sec)") +
    #scale_y_continuous(limits = c(0.0, 0.0002)) +
      ggtitle("") +
      t

#p
# Rotate the box plot
#p + coord_flip()

```

Stacked Bar plot three stages

```{r}
 # library
library(ggplot2)



# Stacked
ggplot(dfTimeStage, aes(fill=Type, y=Time, x=Mode)) + t +
    geom_bar(position="stack", stat="identity")
```

Stacked bar plot for build vs traverse
```{r}
 # library
library(ggplot2)

dfTimeBT <- dfTimeBuildTraverse[dfTimeBuildTraverse$Mode!="naive",]

#Sort factor levels in plot
dfTimeBT$Mode <- factor(dfTimeBT$Mode, levels = c('naive','lbvh','rtx'),ordered = TRUE)

#Rename factor levels
dfTimeBT$Mode <- revalue(dfTimeBT$Mode, c("naive"="Naive", "lbvh"="LBVH", "rtx" = "RTX\n(Ours)"))

scenes <- c("gephi-100k", "k-5-10-connected", "k-5-10-unconnected", "tree16")
for (s in scenes) {
  dfTimeBTS <- dfTimeBT[dfTimeBuildTraverse$Scene==s,]
  # Stacked
  p<-ggplot(dfTimeBTS, aes(fill=Type, y=Time, x=Mode)) + t+ 
      geom_bar(position="stack", stat="identity") +
     labs(x="Implementation", y="Time(sec)") +
     ggtitle(s)
  print(p)
  
  ggsave(paste(s, "-BuildTraverse-StackedBar.pdf", sep=""), p)
}
```

Plot the run time development with increasing an increasing number of node tree4-18
```{r}
library(binr)
library(caret)
library(cowplot)


tSmallAxisLabel <-  theme(axis.text.x=element_text(size=18,face="bold"),
        axis.text.y=element_text(size=18,face="bold"),
        axis.title=element_text(size=26,face="bold"),
        legend.title = element_text(size=22,face="bold"),
        legend.text=element_text(size=20,face="bold"),
        strip.text.x = element_text(size = 22,face="bold"),
        plot.title = element_text(size=24,face="bold"),
        aspect.ratio=1
        )  

scenes = c()
renameMap = c()

for (i in seq(4, 17)) {
  sceneName <- paste("tree", i, sep="")
  scenes <- c(scenes, sceneName)
}
renameMap <- seq(4, 17)
names(renameMap) <- scenes

dfLP <- dfMeans[dfMeans$Scene %in% scenes,]

dfLP$Elapsed <- dfLP$Elapsed * 1000
dfLP$TimeTraverse <- dfLP$TimeTraverse* 1000 
dfLP$TimeBuild <- dfLP$TimeBuild* 1000
dfLP$Scene <- factor(dfLP$Scene, levels = scenes,ordered = TRUE)
dfLP$Scene <- revalue(dfLP$Scene, renameMap)
#Scenes where factors, converting them to numeric lets them range from 1 to n. Hence, we need to add
dfLP$Scene <- as.numeric(dfLP$Scene) + (4-1)
dfLP$Mode <- factor(dfLP$Mode, c("naive", "lbvh", "rtx"),ordered = TRUE)
dfLP$Mode <- revalue(dfLP$Mode, c("naive"="Naive", "lbvh"="LBVH", "rtx" = "RTX (Ours)"))

p1<-ggplot(dfLP, aes(x=dfLP$Scene, y=dfLP$TimeTraverse, group=dfLP$Mode)) +
  geom_line(aes(color=Mode),size=1.6)+
  geom_point(aes(shape=Mode, color=Mode),size=3.5)+
  #coord_cartesian(ylim = c(0, 20)) + 
  #scale_y_continuous(trans='log2') +
  labs(x="Binary Tree Depth", y="Mean Time (ms)") +
  scale_x_continuous(breaks=c(2,4,6,8,10,12,14, 16,18)) + 
  scale_color_manual(values = c("#E7B800", "#2E9FDF", "#FC4E07"))+
  tSmallAxisLabel +
  #theme(legend.position = "none")
  ggsave("tree-traverse-lin.pdf", p1)
#print(p)

p2<-ggplot(dfLP, aes(x=dfLP$Scene, y=dfLP$TimeTraverse, group=dfLP$Mode)) +
  geom_line(aes(color=Mode),size=1.6)+
  geom_point(aes(shape=Mode, color=Mode),size=3.5)+
  #geom_line(aes(linetype=Mode,color=Mode),size=1.4)+
  #geom_point(aes(shape=Mode, color=Mode),size=3.0)+
  #coord_cartesian(ylim = c(0, 20)) + 
  scale_y_continuous(trans='log2') +
  scale_x_continuous(breaks=c(2,4,6,8,10,12,14, 16,18)) + 
  scale_color_manual(values = c("#E7B800", "#2E9FDF", "#FC4E07"))+
#  coord_cartesian(xlim =c(4,18)) +
  labs(x="Binary Tree Depth", y="Mean Time (ms)") +
  #theme(legend.position = "none") +
  tSmallAxisLabel
  ggsave("tree-traverse-log.pdf", p2)
#print(p)


# Generate a list of the aligned plot objects
pl <- align_plots(p1, p2, align="v")

ggdraw(pl[[1]])
#ggsave("tree-traverse-lin.pdf", p1, height = 7 , width = 7 * aspect_ratio)

ggdraw(pl[[2]])
#ggsave("tree-traverse-log.pdf", p2, height = 7 , width = 7 * aspect_ratio)


```



Plot with run time development over time with regression

```{r}
library(binr)
library(caret)


validity <- as.numeric(which(dfA$Mode == "naive"))

df <- dfA[validity,]

par(new=TRUE)
bx_labels=seq(0.0, 1000.0, 50.0)
box_labels <- c()
for (i in 2:length(bx_labels)-1) {
  l <- paste("(", bx_labels[i], ",",  bx_labels[i+1], "]", sep="")
  print(l)
  box_labels <- c(box_labels, l)
}

filtered_data_bins_ <- cut(df$Iteration, breaks=bx_labels)

dif_pred_target <- df$Elapsed

boxplot(dif_pred_target~filtered_data_bins_,data=df, outline=FALSE, ylim=c(0.004,0.05),
    axes = FALSE, ann = FALSE)
#las = 2, ylab="Deviation(m)", xlab="Target Distance Intervals(m)"
#)
## add axes
#axis(1, at = 1:23, labels = box_labels, cex.axis = 1.2, srt = 45, adj = 1,)

#text(seq(1.5,end_point,by=2), par("usr")[3]-0.25, 
#     srt = 60, adj= 1, xpd = TRUE,
#     labels =  box_labels, cex=0.65)

#text(cex=0.65, x=bplt-0.25, y=-1.25, box_labels, xpd=TRUE, srt=45)

axis(1, at = seq(1, length(box_labels)), labels = FALSE)
#- 0.0005
text(x = seq_along(box_labels), y = par("usr")[3] - 0.002, srt = 45, adj = 1,
     labels = box_labels, xpd = TRUE)
axis(2, cex.axis = 0.8)

## now draw the y-axis annotation on a different line out from the plot
## using the extra margin space:
title(ylab = "Run time (sec)", xlab = "", cex.lab = 1.2,
      line = 2.5 )

text(x=12,y=-0.26,"Iteration", cex = 1.0, xpd = TRUE)
## draw the box to finish off
box()

grid(nx=NA, ny=NULL, lwd = 2)
par(new=TRUE)
#boxplot(dif_pred_target~filtered_data_bins_,data=depth_accuracy, outline=FALSE,
#        las = 2,  ylab="Deviation(m)", xlab="Target Distance Intervals(m)"
#        )
means <- tapply(dif_pred_target,filtered_data_bins_,mean)

#plot(x=depth_accuracy$target,y=dif_pred_target)

#validity <- as.numeric(which(filtered_data_bins_ < length(bx_labels)))

#filtered_target = depth_accuracy$target[validity]
#filtered_dif_pref = dif_pred_target[validity]
means_c <- means
rownames(means_c)<-c()
x_pos <- bx_labels[2:21]

df.pred <- data.frame(x_pos, means_c)
colnames(df.pred) <- c("x", "mean")

regmodel <- lm(df.pred$mean ~ df.pred$x)
predicted <- predict(regmodel, data=df.pred)
#x_steps <- seq(0,7, 0.25) * 23
lines(df.pred$x / 6 * 24 -1, predicted, col = "green", lwd = 2)
points(means,col="red",pch=18)
#abline(regmodel, col = "darkgreen", lwd = 3)


```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

